---
title: "Getting Started with Binomial"
author: "Gavril Moniaga"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution

The package `"binomial"` is a compact implementation to compute and visualize attributes of
the binomial distribution.

## Main functions
There are four main functions in this package.

### Choose (n choose k)
Calculates the number of calculates the number of combinations in which `k` successes can occur in `n` trials.

```{r}
bin_choose(n = 5,k = 2)
```

### Probability
Calculates the probability of getting `success` successes in `trials` trials, with probability `prob` of success.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

### Probability Distribution
Generates a data.frame mapping number of successes to the probability of that number of successes.

```{r}
bin_distribution(trials = 5, prob = 0.5)
```

To plot this distribution:

```{r, fig.show='hold'}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

### Cumulative Distribution
Generates a data.frame mapping number of successes to the probability of that number of successes, as well as the cumulative probablility.

```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

To plot this distribution:

```{r, fig.show='hold'}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## Creating a Random Variable `binvar` object

To understand a specific binomial distribution, create a `binvar` object. You can then proceed to view the summary of the variable, including data on the mean, variance, mode, skewness, and kurtosis of the binomial random variable.

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```

## Functions of measures
There are also convenient main functions for each of the summary measures:

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```